Last glacial cycle glacier erosion potential in the Alps \large \newline Supplementary figures

### 2021-06-10 articles/erosion/alps-erosion-supplement.tex
Add volume evolution plots in supplement.

    \begin{figure*}
      \includegraphics{alpero_cumulative}
      \caption[%
        Cumulative erosion potential and annual erosion volume after
        \citet{Koppes.etal.2015}, same as main text Fig. 1.
        ]{%
        \textbf{(a)} Modelled cumulative (time-integrated) glacial erosion
          potential over the last glacial cycle and geomorphological
          reconstruction of Last Glacial Maximum Alpine glacier extent for
          comparison \citep[solid blue line,][]{Ehlers.etal.2011}.
          The background maps consists of the initial basal topography from
          SRTM \citep{Jarvis.etal.2008} and Natural Earth Data
          \citep{Patterson.Kelso.2017}.
        \textbf{(b)} Modelled total ice volume in centimetres of sea-level
          equivalent (cm~s.l.e., black), annual (domain-integrated) potential
          erosion volume (light brown) and its 1-ka running mean (dark brown).
          Shaded gray areas indicate the timing for MIS~2 and~4
          \citep{Lisiecki.Raymo.2005}. Hatches mark periods with ice volume
          below 3\,cm~s.l.e. where glacier sliding may be affected by
          stress-balance approximations and model horizontal resolution.}
        \label{fig:cumulative}
    \end{figure*}

@@

>>>>

    \begin{figure*}
      \includegraphics{alpero_cumulative}
      \caption[%
        Cumulative erosion potential and annual erosion volume after
        \citet{Koppes.etal.2015}, same as main text Fig. 1.
        ]{%
        \textbf{(a)} Modelled cumulative (time-integrated) glacial erosion
          potential over the last glacial cycle and geomorphological
          reconstruction of Last Glacial Maximum Alpine glacier extent for
          comparison \citep[solid blue line,][]{Ehlers.etal.2011}.
          The background maps consists of the initial basal topography from
          SRTM \citep{Jarvis.etal.2008} and Natural Earth Data
          \citep{Patterson.Kelso.2017}.
        \textbf{(b)} Modelled total ice volume in centimetres of sea-level
          equivalent (cm~s.l.e., black), annual (domain-integrated) potential
          erosion volume (light brown) and its 1-ka running mean (dark brown).
          Shaded gray areas indicate the timing for MIS~2 and~4
          \citep{Lisiecki.Raymo.2005}. Hatches mark periods with ice volume
          below 3\,cm~s.l.e. where glacier sliding may be affected by
          stress-balance approximations and model horizontal resolution.
        After \citet{Koppes.etal.2015}, same as main text Fig. 1.}
        \label{fig:cumulative}
    \end{figure*}

@@

    \begin{figure*}
      \begin{minipage}[t]{85mm}
      \includegraphics{alpero_evolution}
      \caption[%
        Potential erosion volume in relation to ice volume after
        \citet{Koppes.etal.2015}, same as main text Fig. 2.
      ]{%
        Modelled annual (domain-integrated) potential erosion volume (light
        curves) and its 1-ka running mean (dark curves) in relation to the
        modelled total ice volume in centimetres of sea-level equivalent. Blue
        indicates increasing ice volume and brown decreasing ice volume.
        After \citet{Koppes.etal.2015}, same as main text Fig. 2.}
      \end{minipage}
      \hfill
      \begin{minipage}[t]{85mm}
      \includegraphics{alpero_evolution_her2015}
      \caption{%
        Potential erosion volume in relation to ice volume after
        \citet{Herman.etal.2015}.}
      \end{minipage}
    \end{figure*}

    \begin{figure*}
      \begin{minipage}[t]{85mm}
      \includegraphics{alpero_evolution_hum1994}
      \caption{%
        Potential erosion volume in relation to ice volume after
        \citet{Humphrey.Raymond.1994}.}
      \end{minipage}
      \hfill
      \begin{minipage}[t]{85mm}
      \includegraphics{alpero_evolution_coo2020}
      \caption{%
        Potential erosion volume in relation to ice volume after
        \citet{Cook.etal.2020}.}
      \end{minipage}
    \end{figure*}
